---
title: 'Quiz #1'
author: "Brandon Güell"
date: "9/26/2017"
output: html_document
---

import hte zombies file
```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)

```
okay so its now a dataframe called d

now i need to wrangle some data!
lets use dpylr!
```{r}
library(dplyr)
summary(d)
df=tbl_df(d)
df
#only get first and last names of females survivors using piping

surf <- df %>% #name it somethign new
  select(first_name, last_name, gender) %>% #select only the colums of names and gender
  filter(gender=="Female") %>% #select rows only where gender==female
  select(first_name, last_name) #then only get teh columns of names... propbably could have done filter FIRST and then this.. but this works i think...
surf

```
extra credit attempt....
```{r}
```


#Quiz #2
```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)

```
ets use dpylr!
```{r}
library(dplyr)
summary(d)
df=tbl_df(d)
df
#only get first and last names of females survivors using piping

surf <- df %>% #name it somethign new
  select(first_name, last_name, height, weight, zombies_killed, gender) %>% #select only the colums of names and gender
  filter(gender=="Female") %>% #select rows only where gender==female
  select(first_name, last_name, height, weight, zombies_killed) #then only get teh columns of names... propbably could have done filter FIRST and then this.. but this works i think...

surf
```


okay so now graph difference betwee zombies killed by height, between geight categories

```{r}
surf=mutate(surf, tall= height>=65 ,short= height<65)
surf
library(tidyr)
#couldn't figure out how to get the two categories....

library(ggplot2)
ggplot(surf, aes(x=height, y=zombies_killed)) +geom_boxplot(aes(color=tall)) #sorta worked.... lol 
```




#quiz 3? idk halloween

med nursing
age and YEO as YEO as cont variable
scatterplot regression line with 95% CI
color points so males are pink and females are blue

```{r}
library(curl)
library(dplyr)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)

surf <- d %>% #name it somethign new
  filter(major=="medicine/nursing") #select rows only where major are nursing/medicine
surf

m=lm(data = surf, age ~ years_of_education)
m
summary(m)

library(ggplot2)
g= ggplot(data=surf, aes(x=age, y=years_of_education, color= gender)) + geom_point() + geom_smooth(method="lm", formula = y ~ x)
g
```

